Supplemental Materials

### 2021-07-23 supplement/supplement-main.Rmd
small tweaks and typos

We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for 200 bootstrapped resamples of the original training data. Figure 3 visualizes the frequency with which each arc appeared in the resulting model across these replicates, and figure \@ref(fig:disp-maingraph) visualizes the model with the coefficients for each link encoded by color.

@@

```{r fig3-disp-bootgraph, echo=F, fig.width=8, fig.height=5, fig.cap="Bootstrapped confidence estimates for Bayesian network edges. Edge color indicates frequency with which edges appeared when conducting search across 200 bootstrap replicates. Only edges appearing in at least 20\\% of graphs are shown. Our primary outcome of interest, vaccination intentions, is highlighted in yellow."}

@@

```{r fig4-disp-maingraph, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions. Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links. Our primary outcome of interest, vaccination intentions, is highlighted in yellow."}

@@

Finally, when asked why most healthcare providers recommend vaccinating young children, most participants (7 of 15; 1 participant did not respond) stated explicitly that healthcare providers have financial incentives to recommend vaccination -- but many (7 of 15, including several who mentioned financial incentives) also acknowledged that healthcare providers likely believe (in the participants’ view, mistakenly) that vaccinations are harmless and effective. Some participants (6 of 15) stated that healthcare providers are following protocol

@@

_Holistic balance_ was the only belief for which we could identify a pre-existing psychometrically valid scale [@mcfadden.etal2010]. For each of the other 13 beliefs, we translated our qualitative insights into new psychometrically-valid scales through an iterative series of pilot studies not described here. We stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable (Cronbach’s $\alpha \geq .80$).

@@

Studies 1-4 were conducted using online surveys (administered with Qualtrics survey software) with participants recruited from Amazon’s mechanical turk (mTurk) work distribution website. All studies were conducted between [dates]. Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4. A total of # participants completed their participation in these studies. All participants had gained approval for ≥ 95% of previous work (≥ 100 assignments); had verified US MTurk accounts; and indicated that they were ≥ 18 years old. See the participant demographics summary section below for full demographic information.

@@

```{r fig7-s2_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow. Right, mean observed and model predicted change scores for the Disease Risk intervention condition. In both plots, error bars represent 95\\% confidence intervals."}
## combined plot for paper
library(patchwork)

@@

```{r fig9-s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow. Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition. In both plots, error bars represent 95\\% confidence intervals."}

@@

```{r fig10-s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow. Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition. In both plots, error bars represent 95\\% confidence intervals."}

@@

We attempted to contact and re-recruit as many of the `r nrow(d_bn)` participants who completed Study 1 to participate in a follow-up study in May of 2019. We were able to re-recruit `r s4_meta$n_recruited` participants and of these`r s4_meta$n_complete` successfully completed the study including passing all attention checks.

@@

```{r fig11-s4_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4. Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York; our primary outcome of interest, vaccination intentions, is highlighted in yellow. Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak. In both plots, error bars represent 95\\% confidence intervals."}

@@

At the beginning of the study, participants read the following instructions: “In this study, you will be asked to read a range of statements. Some of these statements may be controversial, and others less so. We are interested in your opinions about these issues. On each of the following screens, you'll see several statements. Please indicate how much you agree or disagree with each statement.”

Participants then proceeded through 14 pages, with a different scale presented on each page. Scales, and questions within each scale, were presented in a random order for each participant. On each page, participants were asked to rate “how much you agree or disagree” on a 7-point scale from “Strongly disagree” to “Strongly agree.” After completing all 14 scales, participants were asked standard demographics questions (gender, age, race/ethnicity, religious affiliation, educational attainment, annual household income) as well as a handful of questions about whether they were or were expecting to be a parent. The study concluded with a brief statement about the safety of vaccines, as follows: “We very much appreciate hearing your opinions about these various issues. Some of these statements concerned vaccines. The overwhelming consensus in the scientific and medical communities is that vaccines are safe and effective. In case you're interested in learning more about this, below is a statement from the World Health Organization (WHO) on this topic, and a link to their website: ‘Vaccination is one of the most cost-effective health interventions available, saving millions of people from illness, disability and death each year. Effective and safe vaccines, which protect against a number of serious diseases, are available and many promising new vaccines are being developed.’ (WHO Website: www.who.int/immunization/diseases/en/).”

>>>>

We used a bootstrapping procedure to estimate the confidence in each of the links in this model, conducting the structure learning procedure repeatedly for 200 bootstrapped resamples of the original training data. Figure 3 visualizes the frequency with which each arc appeared in the resulting model across these replicates, and Figure 4 visualizes the model with the coefficients for each link encoded by color.

@@

```{r fig3-disp-bootgraph, echo=F, fig.width=8, fig.height=5, fig.cap="Bootstrapped confidence estimates for Bayesian network edges. Edge color indicates frequency with which edges appeared when conducting search across 200 bootstrap replicates. Only edges appearing in at least 20\\% of graphs are shown. Our primary outcome of interest, vaccination intentions, is highlighted in gray."}

@@

```{r fig4-disp-maingraph, echo=F, fig.width=8, fig.height=5, fig.align='center', fig.cap="Bayesian network model of intuitive theory surrounding vaccination decisions. Edge color indicates the magnitude of the generative (blue) or preventive (red) coeffient for the links. Our primary outcome of interest, vaccination intentions, is highlighted in gray."}

@@

Finally, when asked why most healthcare providers recommend vaccinating young children, most participants (7 of 15; 1 participant did not respond) stated explicitly that healthcare providers have financial incentives to recommend vaccination -- but many (7 of 15, including several who mentioned financial incentives) also acknowledged that healthcare providers likely believe (in the participants’ view, mistakenly) that vaccinations are harmless and effective. Some participants (6 of 15) stated that healthcare providers are following protocol.

@@

_Holistic balance_ was the only belief for which we could identify a pre-existing psychometrically valid scale [@mcfadden.etal2010]. For each of the other 13 beliefs, we translated our qualitative insights into new psychometrically-valid scales through an iterative series of pilot studies not described here. We stipulated that each scale should be brief, composed of 4-6 statements for participants to evaluate; include at least one reverse-coded item; and be highly reliable in these pilot studies (observed reliability in final pilot study: all Cronbach’s $\alpha \geq .80$).

@@

Studies 1-4 were conducted using online surveys (administered with Qualtrics survey software) with participants recruited from Amazon’s mechanical turk (mTurk) work distribution website. All studies were conducted between August 2017 and June 2019. Repeat participation was prevented, with no participants involved in more than one study, except as noted in Study 4. A total of # participants completed their participation in these studies. All participants had gained approval for ≥ 95% of previous work (≥ 100 assignments); had verified US MTurk accounts; and indicated that they were ≥ 18 years old. See the participant demographics summary section below for full demographic information.

@@

```{r fig7-s2_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray. Right, mean observed and model predicted change scores for the Disease Risk intervention condition. In both plots, error bars represent 95\\% confidence intervals."}
## combined plot for paper
library(patchwork)

@@

```{r fig9-s3_plot, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray. Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition. In both plots, error bars represent 95\\% confidence intervals."}

@@

```{r fig10-s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in gray. Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition. In both plots, error bars represent 95\\% confidence intervals."}

@@

We attempted to contact and re-recruit as many of the `r nrow(d_bn)` participants who completed Study 1 to participate in a follow-up study in May of 2019. We were able to re-recruit `r s4_meta$n_recruited` participants and, of these, `r s4_meta$n_complete` successfully completed the study including passing all attention checks.

@@

```{r fig11-s4_plot, echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4. Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York; our primary outcome of interest, vaccination intentions, is highlighted in gray. Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak. In both plots, error bars represent 95\\% confidence intervals."}

@@

_Text of the belief scales used in Studies 1-4_

At the beginning of each study, participants read the following instructions: “In this study, you will be asked to read a range of statements. Some of these statements may be controversial, and others less so. We are interested in your opinions about these issues. On each of the following screens, you'll see several statements. Please indicate how much you agree or disagree with each statement.”

Participants then proceeded through 14 pages, with a different scale presented on each page. Scales, and questions within each scale, were presented in a random order for each participant. On each page, participants were asked to rate “how much you agree or disagree” on a 7-point scale from “Strongly disagree” to “Strongly agree.” After completing all 14 scales, participants were asked standard demographics questions (gender, age, race/ethnicity, religious affiliation, educational attainment, annual household income) as well as a handful of questions about whether they were or were expecting to be a parent.

In Study 1, but not Studies 2-4, the study concluded with a brief statement about the safety of vaccines, as follows: “We very much appreciate hearing your opinions about these various issues. Some of these statements concerned vaccines. The overwhelming consensus in the scientific and medical communities is that vaccines are safe and effective. In case you're interested in learning more about this, below is a statement from the World Health Organization (WHO) on this topic, and a link to their website: ‘Vaccination is one of the most cost-effective health interventions available, saving millions of people from illness, disability and death each year. Effective and safe vaccines, which protect against a number of serious diseases, are available and many promising new vaccines are being developed.’ (WHO Website: www.who.int/immunization/diseases/en/).”
